Log Journal Project Theme 9

### 2022-10-28 LogJournal.Rmd
Added a TOC and finished the logjournal

---
title: 'Log Journal Project Theme 9'
author: 'J.A. Busker (352905 BFV3)'
output:
  pdf_document: 
    pandoc_args: --highlight=breezedark
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA)
library(tidyr)
library(kableExtra)
library(ggplot2)
library(gridExtra)
library(cowplot)
library(ggpubr)
library(pander)
library(ggbiplot)
library(reshape2)
library(ggfortify)
library(ggalt)
library(ggridges)
library(cluster)
```

@@

---

## EDA of yeast data: Protein Localization

The data has been retrived from [uci.](https://archive.ics.uci.edu/ml/datasets/Yeast) The dataset has been gathered of 1484 yeast sequences from SWISS-PROT using the annotations from YPD.

@@

### Codebook

Since there is not a codebook. I created my own codebook.

@@

### Load the data

@@

The yeast data set contains scores per cellular localization sites.

### Clean the data

@@

@@

### Univariate Analysis

@@

### Bivariate Analysis

@@

The long calculated correlation matrix.

@@

### Class labels

@@

### Multivariate analysis

@@

# MIL algorithms

@@

**Criteria for MIL algorithms**

>>>>

---
output:
  pdf_document:
    pandoc_args: --highlight=breezedark
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA)
```

@@

# Machine Learning Research log

## Can machine learning predict protein localization based on their aminoacid sequences

\vspace*{\fill}
\begin{flushright}
John Busker\\
352905\\
Bio-Informatics\\
Dave Langers, and Bart Barnard\\
28-10-2022
\end{flushright}

# Table of Contents

1. [R Environment](#r-environment) \dotfill 3

2. [EDA](#eda) \dotfill 4  
  2.1 [About The Data](#about-the-data) \dotfill 4  
  2.2 [Codebook](#codebook) \dotfill 5  
  2.3 [Loading The Data](#loading-the-data) \dotfill 6  
  2.4 [Cleaning The Data](#cleaning-the-data) \dotfill 6  
  2.5 [Data Transformation](#data-transformation) \dotfill 9  
  2.6 [Univariate Analysis](#univariate-analysis) \dotfill 9  
  2.7 [Bivariate Analysis](#bivariate-analysis) \dotfill 12   
  2.8 [Class Labels](#class-labels) \dotfill 15  
  2.9 [Multivariate Analysis](#multivariate-analysis) \dotfill 18

3. [MIL Algorithms](#mil-algorithms) \dotfill 20  
  3.1 [Criteria For MIL Algorithms](#criteria-for-mil-algorithms) \dotfill 20

# R Environment

Multiple libraries have been uses for data analysis and further processes. The libraries used are:

```{r setup, message=FALSE}
library(tidyr)
library(kableExtra)
library(ggplot2)
library(gridExtra)
library(cowplot)
library(ggpubr)
library(pander)
library(ggbiplot)
library(reshape2)
library(ggfortify)
library(ggalt)
library(ggridges)
library(cluster)
```

# EDA

## About The Data

The data has been retrieved from [uci.](https://archive.ics.uci.edu/ml/datasets/Yeast) The dataset consists of 1484 yeast sequences from SWISS-PROT using the annotations from YPD. In this section, we are going to talk about the results we found from the dataset. Eight features were used in classification: the presence or absence of an HDEL pattern as a signal for retention in the endoplasmic reticulum lumen (erl); The results of discriminant analysis on the amino acid content of vacuolar and extracellular proteins (vac); the result of discriminant analysis on the amino acid composition of the 20-residue N-terminal region of mitochondrial and non-mitochondrial proteins (mit); the presence or absence of nuclear localization consensus patterns combined with a term reflecting the frequency of basic residues (nuc); and some combination of the presence of a short sequence motif and the result of discriminant analysis of the amino acid composition of the protein sequence (pox).

@@

Yeast proteins were classified into ten classes: **cytoplasmic:** cytoskeletal (CYT); nuc]ear (NUC); vacuolar (VAC); mitochondrial (MIT); isomal (POX); **extracellular:** including those localized against the cell wall (EXC); proteins localized to the lumen of the endoplasmic reticulum (ERL); membrane proteins with a cleaved signal (ME1); membrane proteins with an uncleared signal (ME2); and membrane proteins with no N-terminal sign (ME3), where ME1, ME2,and ME3 proteins may be localized to the plasma membrane, the endoplasmic reticulum membrane, or the membrane of a golgi body.

## Codebook

Since there is not a codebook. A own codebook has been created

@@

## Loading The Data

@@

The yeast data set contains scores per cellular localization sites. The last column is the sequence's localization site. There are ten different possibilities for this.

## Cleaning The Data

@@

## Data Transformation

@@

## Univariate Analysis

@@

## Bivariate Analysis

@@

The long calculated correlation matrix. Let's visualise this using a heatmap.

@@

## Class Labels

@@

## Multivariate analysis

@@

# MIL Algorithms

@@

## Criteria For MIL Algorithms
